### 2022-08-05 thesis/appendix.tex
Draft of RT reachability written
Second draft of thesis finished
Committing old format slides and more changes to thesis

\chapter{Benchmark Model Definitions}
\label{app:benchmark}

\section{Vanderpol Oscillator}
The Vanderpol Oscillator is a classical two-dimensional non-linear dynamical system governed by the following dynamics:
\begin{equation}
  \begin{cases}
  x' = y \\
  y' = \mu \cdot(1 - x^2)\cdot y - x
  \end{cases}
 \end{equation}

@@

\section{Coupled Vanderpol}
This model couples two Vanderpol Oscillators together, resulting in an non-linear ODE of four variables
\begin{equation}
  \begin{cases}
  x_1' = y_1\\
  y_1' = (1-x_1^2)\cdot y_1 - x_1 + (x_2 - x_1) \\
  x_2 ' = y_2 \\
  y_2' = (1-x_2^2)\cdot y_2 - x_2 + (x_1 - x_2)
  \end{cases}
 \end{equation}
\noindent This model was investigated in \cite{rand1980bifurcation}, and the dynamics were gathered from \cite{aachen}

>>>>

\chapter{Additional Benchmark Model Definitions}
\label{app:benchmark}

\section{Vanderpol Oscillator}
\label{sec:vdp}
The Vanderpol Oscillator is a classical two-dimensional non-linear dynamical system governed by the following dynamics:
\begin{equation}
  \begin{cases}
  x' = y \\
  y' = \mu \cdot(1 - x^2)\cdot y - x
  \end{cases}
 \end{equation}

@@

\section{Coupled Vanderpol}
\label{sec:cvdp}
This model couples two Vanderpol Oscillators together, resulting in an non-linear ODE of four variables
\begin{equation}
  \begin{cases}
  x_1' = y_1\\
  y_1' = (1-x_1^2)\cdot y_1 - x_1 + (x_2 - x_1) \\
  x_2 ' = y_2 \\
  y_2' = (1-x_2^2)\cdot y_2 - x_2 + (x_1 - x_2)
  \end{cases}
 \end{equation}
\noindent This model was investigated in \cite{rand1980bifurcation}, and the dynamics were gathered from \cite{aachen}

### 2022-08-05 thesis/formats.tex
Committing old format slides and more changes to thesis

\section{Local Linear Approximations}
\label{sec:lin_app}
%
Intuitively speaking, if time step is discretized to be sufficiently small, propagating trajectories according to the non-linear dynamics $f$ for one time step could lead to good lienar approximations of the dynamics within a small region.
%
%
To do this, we first sample a set of points in the parallelotope bundle called \emph{support points} and propagate them to the next step using the dynamics $f$.
%
Support points are a subset of the vertices of the parallelotope that either maximize or minimize the template directions over the parallelotope bundle.
%
That is the support points are the set of points $P_{supp}$ defined as:
\begin{equation}
\label{eq:support}
 P_{supp} = \bigcup_{i=1}^n \{ \max_{x \in Q} \Lambda^Q_i\cdot x, \; \min_{x \in Q} \Lambda^Q_i\cdot x \}
\end{equation}
%
for all template directions of the bundle $\Lambda^Q_i$. We use the support points as a data-driven approach to find the best-fit linear function to use. All points are found by a straightforward linear program.
%
%In this case, for small time steps a nonlinear function can be approximated fairly accurately by a linear transformation.
%
To find the approximate linear transformation, let $x_i$ denote the support points calculated by Equation \ref{eq:support}. We perform the following least-squares procedure: the objective would be to find an linear transformation $A$ such that it minimizes the following objective function:
\begin{equation}
  \label{eq:least_squares}
  \min_{A} \sum_{x_i} ||f(x_i) - Ax_i||^2_2
\end{equation}
%
where $||\cdot||_2$ is the standard Euclidean norm on $\reals^n$.
%
If the dynamics of a system are linear, i.e., $x^{+} = Ax$, the image of the parallelotope $c_{l} \leq \Lambda x \leq c_{u}$, is the set $c_{l} \leq \Lambda \cdot A^{-1} x \leq c_{u}$.
%
Therefore, given the template directions of the initial set as $\T_0$, we compute the local linear approximation of the non-linear dynamics and change the template directions by multiplying them with the inverse of the approximate linear dynamics.
%
%This will reflect the approximate template directions for one step forward. To continue to
%

>>>>

\section{Drawbacks to the Static Algorithm}
Before we embark on introducing the dynamic algorithm, let us first consider a few motivating factors.
%
As discussed in Section \ref{sec:static}, the static algorithm requires template directions to be specified by the user in order for the reachable set computation to proceed.
%
The parallelotopes tended to be defined by a combination of axis-aligned directions or diagonal directions.
%
However, it is unclear whether these template directions work reasonably well over general non-linear dynamics.
%
This is a problem which has profound consequences for computing useful over-approximations.
%
Choosing the incorrect directions could very well lead to an over-approximation too conservative for any practical use.
%
Figure \ref{fig:bloat_cvdp} portrays a simple example of a reachable set whose wrapping error becomes explosive after a few steps.
%
In light of these ramifications, it is esstentially incumbent on the user to choose fruitful template directions that control the growth of the over-approximation.
%
Due to the inherent difficult nature of choosing these template directions, it may be unreasonable to delegate this responsibility to a practitioner who knows little about parallelotope-based reachability.
%
These drawbacks to the static algorithm motivate the rationale behind the \emph{automatic} aspect of our modified algorithm.

Additionally, as the template directions are set at the beginning before the reachable set computation proceeds, these directions cannot adapt to the dynamics as the computation executes.
%
There may be template directions which may yield much leaner over-approximations at an intermediate step during the computation.
%
Hence, the ability to change the composition of the parallelotope bundle by adding and removing parallelotopes based on a data-driven approach could yield leaner over-approximations.
%
These considerations motivate the rationale behind the \emph{dynamic} aspect of our modified algorithm.

\begin{figure}[t!]
\centering
\includegraphics[width= 0.9\textwidth]{figures/cvdp20.png}
\caption{Consequences of choosing inappropriate template directions as demonstrated by the Coupled Vanderpol model. See Section \ref{sec:cvdp} for the model definition.}
\label{fig:bloat_cvdp}
\end{figure}

\section{Local Linear Approximations}
\label{sec:lin_app}
%
Intuitively speaking, if time step is discretized to be sufficiently small, propagating trajectories according to the non-linear dynamics $f$ for one time step could lead to good lienar approximations of the dynamics within a small region.
%
%
To do this, we first sample a set of points in the parallelotope bundle called \emph{support points} and propagate them to the next step using the dynamics $f$.
%
Support points are a subset of the vertices of the parallelotope that either maximize or minimize the template directions over the parallelotope bundle.
%
That is the support points are the set of points $P_{supp}$ defined as:
\begin{equation}
\label{eq:support}
 P_{supp} = \bigcup_{i=1}^n \{ \max_{x \in Q} \Lambda^Q_i\cdot x, \; \min_{x \in Q} \Lambda^Q_i\cdot x \}
\end{equation}
%
for all template directions of the bundle $\Lambda^Q_i$. We use the support points as a data-driven approach to determine the best-fit linear function to use. All points are found by a straightforward linear program.
%
%In this case, for small time steps a nonlinear function can be approximated fairly accurately by a linear transformation.
%
To find the approximate linear transformation, let $x_i$ denote the support points calculated by Equation \ref{eq:support}. We perform the following least-squares procedure: the objective would be to find an linear transformation $A$ such that it minimizes the following objective function:
\begin{equation}
  \label{eq:least_squares}
  \min_{A} \sum_{x_i} ||f(x_i) - Ax_i||^2_2
\end{equation}
%
where $||\cdot||_2$ is the standard Euclidean norm on $\reals^n$.
%
If the dynamics of a system are linear, i.e., $x^{+} = Ax$, the image of the parallelotope $c_{l} \leq \Lambda x \leq c_{u}$, is the set $c_{l} \leq \Lambda \cdot A^{-1} x \leq c_{u}$.
%
To see this, recall the constraint associated to the half-space representation (Definition \ref{def:halfspace_def} and Equation \ref{eq:halfspaceconst}). If we set our new template directions to be $\Lambda \cdot A^{-1}$, the image points of $A$ which satisfy the half-space constraint according to fixed offset vectors $c_l, c_u$ should be:
 \[ c_l \leq (\Lambda \cdot A^{-1})Ax \leq c_u \implies c_{l} \leq \Lambda x \leq c_{u} \]
%
This is satisfied by all the points defining parallelotope $P$ as desired. Therefore, the new template directions will exactly define the image of $P$ under linear dynamics. To exploit this property, given the template directions of the initial set as $\T_0$, we compute the local linear approximation of the non-linear dynamics and change the template directions by multiplying them with the inverse of the approximate linear dynamics.
%
%This will reflect the approximate template directions for one step forward. To continue to
%

### 2022-08-05 thesis/prelim.tex
Committing old format slides and more changes to thesis

  \begin{figure}[h!]
    \centering
    \begin{tikzpicture}
      \draw[step=1cm,gray,very thin, style=help lines] (-3,-3) grid (3,3);
      \draw[fill=blue!40!white, opacity=0.4] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
      \draw[->, thick] (0.5,0.5) -- (1,1) node[above] {$[1,1]$};
      \draw[->, thick] (-0.5,-0.5) -- (-1,-1) node[below] {$[-1,-1]$};
      \draw[->, thick] (-0.5,0.5) -- (-1,1) node[above] {$[-1,1]$};
      \draw[->, thick] (0.5,-0.5) -- (1,-1) node[below] {$[1,-1]$};
      \draw[fill] (0,0) circle [radius=1pt];
      \node[above] {$\mathcal{O}$};
    \end{tikzpicture}
    \caption{Plot of the rotated parallelotope of Example \ref{ex:simple_diag_ptope}. Once again, note the manner in which the template directions and their negative counterparts define parallel planes and the parallelotope's definition as the intersection of the postive and negative half-spaces of all pairs of parallel planes. Once again, $\mathcal{O}$ represents the origin $(0,0)$ and each side of a grid cell represents one unit of distance.}
    \label{fig:diagonal_ptope}
  \end{figure}
\end{example}

@@

\begin{example}
Let us return to the axis-aligned box considered in Example \ref{ex:simple_ptope}.
%
To obtain the anchor, we end up with the trivial solution $x = 1, y=1$ by adhering to Step 1. Hence, the anchor is set to $v = (1,1)$.
%
Subsequently, we solve for the two other vertices by following Step 2 to obtain $x=2, y= 1$ and $x=1,y=2$.
%
By Step 3, this would imply that the two generators are $g_1 = (2,1)-(1,1) = (1,0)$ and $g_2 = (1,2)-(1,1) = (0,1)$.
%
Now combine the anchor and generators to get the generator representation for this paralellotope:
%
\begin{equation}
 P = (1,1) + \alpha_1\cdot(1,0) + \alpha_2\cdot(0,1) \quad \alpha_1, \alpha_2 \in [0,1]
\end{equation}
%
This is exactly the unit box $[0,1]^2$ with its corner at the origin shifted to $(1,1)$.
\end{example}
%
\begin{example}
\label{ex:diag_ptope}
Once again, consider the space $\reals^2$ and the parallelotope $P$ given in half-plane representation as $0 \leq x-y \leq 1$, $0 \leq y \leq 1$.
%
This is a parallelotope with vertices at $(0,0)$, $(1,0)$, $(2,1)$, and $(1,1)$.
%
In the half-space representation, the template directions of the parallelotope $P$ are given by the directions $[1, -1]$ and $[0, 1]$.
%
The half-space representation in matrix form is given as follows:
%
\begin{equation}
  \begin{bmatrix} 0 \\ 0 \end{bmatrix} \leq \begin{bmatrix*}[r]  1 & -1 \\ 0 &  1 \end{bmatrix*}  \begin{bmatrix} x \\ y \end{bmatrix} \leq \begin{bmatrix} 1 \\ 1 \end{bmatrix}. \label{eq:ptopeexample}
\end{equation}
%
To compute the generator representation of $P$, we need to compute the \emph{anchor} and the \emph{generators}.
%
The anchor is obtained by solving the linear equations $x-y = 0, y = 0$.
%
Therefore, the anchor $a$ is the vertex at origin $(0,0)$
%
To compute the two generators of the parallelotope, we compute two vertices of the parallelotope.
%
Vertex $v_1$ is obtained by solving the linear equations $x - y = 1, y = 0$.
%
Therefore, vertex $v_1$ is the vertex $(1,0)$.
%
Similarly, vertex $v_2$ is obtained by solving the linear equations $x-y = 0, y = 1$.
%
Therefore, $v_2$ is the vertex $(1,1)$.
%
The generator $g_1$ is the vector $v_1 - a$, that is $(1,0)- (0,0) = (1,0)$
%
The generator $g_2$ is the vector $v_2 - a$, that is $(1,1) - (0,0) = (1,1)$.
%
Therefore, all the points in the paralellotope can be written as $(x,y) = (0,0) + \alpha_1 \cdot (1,0) + \alpha_2\cdot (1,1)$, $\alpha_1, \alpha_2 \in [0,1]$.
\end{example}
%
The reachable set will be expressed an intersection of parallelotopes. These parallelotopes will be encoded into a parallelotope bundle.
%
\begin{definition}
A \emph{parallelotope bundle} $Q$ is a set of parallelotopes $\{P_0, \ldots, P_m\}$ such that
  $$ Q = \bigcap_{i=1}^{m}P_i $$.
\end{definition}

@@

%--------------------------------------------------------------------------------------------------------------------------------------------------------- --------
\subsection{Bernstein Polynomials}
\label{sec:bernstein}
In this section, we define Bernstein polynomials and state some of their enclosure properties. A \emph{multi-index} ${\bf i}$ of length $n$ is defined as tuple of $n$ elements ${\bf i} = (i_1,\cdots, i_n)$ such that each $i_k \in \mathbb{N}$. Furthermore, we order the multi-indices as follows: if ${\bf i}$ and ${\bf j}$ are two multi-indices of length $n$, then
\[
  {\bf i} \leq {\bf j} \iff i_k \leq j_k, \quad 1 \leq  k \leq n
\]
Finally, we generalize the product of binomial coefficients over multi-indices as:
\[
  \binom{\boldi}{\boldj} := \prod_{k=1}^n \binom{i_k}{j_k}
\]
%
Given two multi-indices $\boldi$ and $\boldd$ of size $n$, where $\boldi \leq \boldd$, the Bernstein basis polynomial of degree $\boldd$ and index $\boldi$ is defined as:
\begin{equation}
\label{eq:bernstein_basis_poly}
\mathcal{B}_{(\boldi,\boldd)}(\boldx) = \beta_{i_1,d_1}(x_1) \beta_{i_2,d_2}(x_2)\ldots \beta_{i_n,d_n}(x_n).
\end{equation}
%
where for $i,d \in \mathbb{N}$ and $x \in \reals$:
%
\begin{equation}
\beta_{i,d}(x) = \binom{d}{i}x^{i}(1-x)^{d - i}
\end{equation}
%
Let $p: \reals^n \rightarrow \reals$ be a real polynomial of degree at most $\boldd$. We can express $p$ as a linear combination of monomials of degree at most $\boldd$:
\[
p(\boldx) = \sum_{\boldi \leq \boldd} a_\boldi \cdot \boldx^\boldi
\]
where $\boldx^\boldi$ represents the monomial $x_1^{i_1}x_2^{i_2}\cdots x_n^{i_n}$. One of the most important properties of Berstein polynomials is that the Bernstein basis polynomials of degree $\boldd$ span the vector space of real multivariate polynomials of degree at most $\boldd$:

\begin{property}
\label{prop:bern_basis}
Every real polynomial $p$ of degree at most $\boldd$ can be represented as linear combination of Bernstein basis polynomials of degree $\boldd$:
%
\begin{equation}
  \label{eq:bernstein_coeff}
  p(\boldx) = \sum_{\boldi \leq \boldd} b_{\boldi} \cdot \mathcal{B}_{(\boldi,\boldd)}(\boldx)
\end{equation}
where $b_\boldi$ denotes the \emph{$\boldi^{th}$ Bernstein Coefficient}:

@@

\noindent In other words, given a polynomial $p(x_1,\ldots,x_n) = \sum_{j \in J} a_j {\bf x}_{j}$ where $J$ is a set of multi-indices iterating through the degrees found in $p$ with $a_j \in \mathbb{R}$, then $p(x_1,\ldots,x_n)$ can be converted into its counterpart under the Bernstein basis, $p(x_1,\ldots,x_n) = \sum_{j \in J} b_j \mathcal{B}_j $ where $b_j$ are the corresponding Bernstein coefficients.

>>>>

  \begin{figure}[h!]
    \centering
    \begin{tikzpicture}
      \draw[step=1cm,gray,very thin, style=help lines] (-3,-3) grid (3,3);
      \draw[fill=blue!40!white, opacity=0.4] (1,0) -- (0,1) -- (-1,0) -- (0,-1) -- cycle;
      \draw[->, thick] (0.5,0.5) -- (1,1) node[above] {$[1,1]$};
      \draw[->, thick] (-0.5,-0.5) -- (-1,-1) node[below] {$[-1,-1]$};
      \draw[->, thick] (-0.5,0.5) -- (-1,1) node[above] {$[-1,1]$};
      \draw[->, thick] (0.5,-0.5) -- (1,-1) node[below] {$[1,-1]$};
      \draw[fill] (0,0) circle [radius=1pt];
      \node[above] {$\mathcal{O}$};
    \end{tikzpicture}
    \caption{Plot of the rotated parallelotope of Example \ref{ex:simple_diag_ptope}. Note the manner in which the template directions and their negative counterparts define parallel planes and the parallelotope's definition as the intersection of the postive and negative half-spaces of all pairs of parallel planes. $\mathcal{O}$ represents the origin $(0,0)$ and each side of a grid cell represents one unit of distance.}
    \label{fig:diagonal_ptope}
  \end{figure}
\end{example}

@@

\begin{example}
Let us return to the axis-aligned box considered in Example \ref{ex:simple_ptope}.
%
To obtain the anchor, we end up with the trivial solution $x = 1, y=1$ by adhering to Step 1. Hence, the anchor is set to $v = (1,1)$.
%
Subsequently, we solve for the two other vertices by following Step 2 to obtain $x=2, y= 1$ and $x=1,y=2$.
%
By Step 3, this would imply that the two generators are $g_1 = (2,1)-(1,1) = (1,0)$ and $g_2 = (1,2)-(1,1) = (0,1)$.
%
Now combine the anchor and generators to get the generator representation for this paralellotope:
%
\begin{equation}
 P = (1,1) + \alpha_1\cdot(1,0) + \alpha_2\cdot(0,1) \quad \alpha_1, \alpha_2 \in [0,1]
\end{equation}
%
This is exactly the unit box $[0,1]^2$ with its corner at the origin shifted to $(1,1)$.
\end{example}
%
\begin{example}
\label{ex:diag_ptope}
Parallelotope $P$ is given in half-plane representation as $0 \leq x-y \leq 1$, $0 \leq y \leq 1$.
%
This is a parallelotope with vertices at $(0,0)$, $(1,0)$, $(2,1)$, and $(1,1)$.
%
The template directions of the parallelotope $P$ are given by the directions $[1, -1]$ and $[0, 1]$.
%
The half-space representation in matrix form is given as follows:
%
\begin{equation}
  \begin{bmatrix} 0 \\ 0 \end{bmatrix} \leq \begin{bmatrix*}[r]  1 & -1 \\ 0 &  1 \end{bmatrix*}  \begin{bmatrix} x \\ y \end{bmatrix} \leq \begin{bmatrix} 1 \\ 1 \end{bmatrix}. \label{eq:ptopeexample}
\end{equation}
%
To compute the generator representation of $P$, we need to compute the \emph{anchor} and the \emph{generators}.
%
The anchor is obtained by solving the linear equations $x-y = 0, y = 0$.
%
Therefore, the anchor $a$ is the vertex at origin $(0,0)$
%
To compute the two generators of the parallelotope, we compute two vertices of the parallelotope.
%
Vertex $v_1$ is obtained by solving the linear equations $x - y = 1, y = 0$.
%
Therefore, vertex $v_1$ is the vertex $(1,0)$.
%
Similarly, vertex $v_2$ is obtained by solving the linear equations $x-y = 0, y = 1$.
%
Therefore, $v_2$ is the vertex $(1,1)$.
%
The generator $g_1$ is the vector $v_1 - a$, that is $(1,0)- (0,0) = (1,0)$
%
The generator $g_2$ is the vector $v_2 - a$, that is $(1,1) - (0,0) = (1,1)$.
%
Therefore, all the points in the paralellotope can be written as $(x,y) = (0,0) + \alpha_1 \cdot (1,0) + \alpha_2\cdot (1,1)$, $\alpha_1, \alpha_2 \in [0,1]$.
%
Figure \ref{fig:diag_ptope} portrays a visual plot of the derived generator representation.
\end{example}

\begin{figure}[h!]
  \centering
  \begin{tikzpicture}
    \draw[step=1cm,gray,very thin, style=help lines] (-3,-3) grid (3,3);
    \draw[fill=blue!40!white, opacity=0.4] (0,0) -- (1,0) -- (2,1) -- (1,1) -- cycle;
    \draw[fill] (0,0) circle [radius=1pt];
    \node[above] {$\mathcal{O}$};

    \draw[fill] (0,0) circle [radius=1.5pt];
    \node[below] at (0,0) {$v$};

    \draw[->, very thick, draw=red] (0,0) -- (1,0) node[midway, below] {$g_1$};
    \draw[->, very thick, draw=red] (0,0) -- (1,1) node[midway, right] {$g_2$};
  \end{tikzpicture}
  \caption{Plot of the generator representation for Example \ref{ex:diag_ptope}. The vertex $v$ represents the anchor while the two vectors $g_1,g_2$ are the generator vectors.}
  \label{fig:diag_ptope}
\end{figure}

%
The reachable set will be expressed an intersection of parallelotopes. These parallelotopes will be encoded into a parallelotope bundle.
%
\begin{definition}
A \emph{parallelotope bundle} $Q$ is a set of parallelotopes $\{P_0, \ldots, P_m\}$ such that
  $$ Q = \bigcap_{i=1}^{m}P_i $$.
\end{definition}

@@

%--------------------------------------------------------------------------------------------------------------------------------------------------------- --------
\newpage
\subsection{Bernstein Polynomials}
\label{sec:bernstein}
In this section, we define Bernstein polynomials and state some of their enclosure properties. A \emph{multi-index} ${\bf i}$ of length $n$ is defined as tuple of $n$ elements ${\bf i} = (i_1,\cdots, i_n)$ such that each $i_k \in \mathbb{N}$. Furthermore, we order the multi-indices as follows: if ${\bf i}$ and ${\bf j}$ are two multi-indices of length $n$, then
\[
  {\bf i} \leq {\bf j} \iff i_k \leq j_k, \quad 1 \leq  k \leq n
\]
Finally, we generalize the product of binomial coefficients over multi-indices as:
\[
  \binom{\boldi}{\boldj} := \prod_{k=1}^n \binom{i_k}{j_k}
\]
%
Given two multi-indices $\boldi$ and $\boldd$ of size $n$, where $\boldi \leq \boldd$, the Bernstein basis polynomial of degree $\boldd$ and index $\boldi$ is defined as:
\begin{equation}
\label{eq:bernstein_basis_poly}
\mathcal{B}_{(\boldi,\boldd)}(\boldx) = \beta_{i_1,d_1}(x_1) \beta_{i_2,d_2}(x_2)\ldots \beta_{i_n,d_n}(x_n).
\end{equation}
%
where for $i,d \in \mathbb{N}$ and $x \in \reals$:
%
\begin{equation}
\beta_{i,d}(x) = \binom{d}{i}x^{i}(1-x)^{d - i}
\end{equation}
%
Let $p: \reals^n \rightarrow \reals$ be a real polynomial of degree at most $\boldd$. We can express $p$ as a linear combination of monomials of degree at most $\boldd$:
\[
p(\boldx) = \sum_{\boldi \leq \boldd} a_\boldi \cdot \boldx^\boldi
\]
where $\boldx^\boldi$ represents the monomial $x_1^{i_1}x_2^{i_2}\cdots x_n^{i_n}$. One of the most important properties of Berstein polynomials is that the Bernstein basis polynomials of degree $\boldd$ span the vector space of real multivariate polynomials of degree at most $\boldd$:
%
In other words, given a polynomial $p(x_1,\ldots,x_n) = \sum_{j \in J} a_j {\bf x}_{j}$ where $J$ is a set of multi-indices iterating through the degrees found in $p$ with $a_j \in \mathbb{R}$, then $p(x_1,\ldots,x_n)$ can be converted into its counterpart under the Bernstein basis, $p(x_1,\ldots,x_n) = \sum_{j \in J} b_j \mathcal{B}_j $ where $b_j$ are the corresponding Bernstein coefficients.
\newpage
\begin{property}
\label{prop:bern_basis}
Every real polynomial $p$ of degree at most $\boldd$ can be represented as linear combination of Bernstein basis polynomials of degree $\boldd$:
%
\begin{equation}
  \label{eq:bernstein_coeff}
  p(\boldx) = \sum_{\boldi \leq \boldd} b_{\boldi} \cdot \mathcal{B}_{(\boldi,\boldd)}(\boldx)
\end{equation}
where $b_\boldi$ denotes the \emph{$\boldi^{th}$ Bernstein Coefficient}:

@@

### 2022-08-05 thesis/staticalg.tex
Committing old format slides and more changes to thesis

Equation~\ref{eq:maxalpha} is a form of $\mathsf{optBox(\Lambda_{i} \cdot f)}$ over $[0,1]^n$.
%
One can compute an upper-bound to this non-linear optimization by computing the Bernstein coefficients of $\Lambda_i \cdot f(a + \Sigma_{i=1}^{n} \alpha_i g_i)$ and taking the maximum and minimum coefficients as shown in Property~\ref{prop:bern_enclosure}.
%
Similarly, we compute the lower-bound of $\Lambda_{i}\cdot f(x)$ for all $x \in P$ by computing the upper-bound of $-1 \times \Lambda_{i}\cdot f(x)$.
%
\begin{remark}
The original algorithm using Bernstein expansion proposed by \cite{dreossi2016parallelotope} assumed polynomial dynamics i.e $f$ is polynomial in the system variables.
%
This is to ensure that a $\Lambda_{i}\cdot f(x)$ is a polynomial after the composition shown in Equation \ref{eq:maxalpha}. Proper Bernstein expansion of this polynomial allows us to exploit the enclosure property of Bernstein coefficients. However, the use of other non-linear optimization solvers, such as Kodiak \cite{kodiak}, allows us to use more general dynamics involving trigonometric and root functions. A Taylor expansion of any analytic function can also be truncated to some suffciently large degree to admit a power series expansion.
\end{remark}

>>>>

Equation~\ref{eq:maxalpha} is a form of $\mathsf{optBox(\Lambda_{i} \cdot f)}$ over $[0,1]^n$.
%
One can compute an upper-bound to this non-linear optimization by computing the Bernstein coefficients of $\Lambda_i \cdot f(a + \Sigma_{i=1}^{n} \alpha_i g_i)$ and taking the maximum and minimum coefficients as shown in Property~\ref{prop:bern_enclosure}.
%
Similarly, we compute the lower-bound of $\Lambda_{i}\cdot f(x)$ for all $x \in P$ by computing the upper-bound of $-1 \times \Lambda_{i}\cdot f(x)$.
%
\begin{remark}
The original algorithm exploiting Bernstein expansion was proposed by \cite{dreossi2016parallelotope} and assumed polynomial dynamics i.e $f$ is polynomial in the system variables.
%
This is to ensure that a $\Lambda_{i}\cdot f(x)$ is a polynomial after the composition shown in Equation \ref{eq:maxalpha}. Proper Bernstein expansion of this polynomial allows us to exploit the enclosure property of Bernstein coefficients. However, the use of other non-linear optimization solvers, such as Kodiak \cite{kodiak}, allows us to use more general dynamics involving trigonometric and root functions. A Taylor expansion of any analytic function can also be truncated to some suffciently large degree to admit a power series expansion.
\end{remark}
